Teaching

### 2025-02-22 teaching.qmd
update

I am external examiner at the University of Manchester (2023 -  ) for their [MSc MSc Computational and Corpus Linguistics.](https://www.manchester.ac.uk/study/masters/courses/list/21198/msc-computational-and-corpus-linguistics/course-details/)

I am external examiner at the University of Glasgow (2022-2025) for their microcredential course in [Applied data skills for processing and presenting data](https://www.gla.ac.uk/coursecatalogue/course/?code=PSYCH2016).

>>>>

I was external examiner at the University of Glasgow (2022-2025) for their microcredential course in [Applied data skills for processing and presenting data](https://www.gla.ac.uk/coursecatalogue/course/?code=PSYCH2016).

I was external examiner at the University of Manchester (2023) for their new [MSc MSc Computational and Corpus Linguistics.](https://www.manchester.ac.uk/study/masters/courses/list/21198/msc-computational-and-corpus-linguistics/course-details/)
